The Heavy Photon Search Test Detector

### 2014-03-08 hps-testrun-nim.tex
Shrinking the rest of the SVT sections: components, svt daq, assembly and alignment

\subsection{Layout}
The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
Each of the layers is comprised of a pair of closely-spaced silicon microstrip sensors mounted back-
to-back to form a module. A 100~mrad stereo angle is used in the first three layers to provide higher-
resolution 3D space points for vertexing.  Using 50~mrad in the last two layers breaks the tracking 
degeneracy of having five identical layers and minimizes fakes from ghost hits to improve pattern 
recognition. Altogether, this layout comprises 20 sensors and hybrids and 100 APV25 chips for a 
total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\footnotesize
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{\small Layout of the SVT.}
}
\label{tab:trk}
\vspace*{-15mm}
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
\includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{\small A rendering of the SVT showing the modules on their support plates held by the 
hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the 
hybrid readout boards in green. The beam enters from the right through a vacuum box with flanges 
for services. }
\label{fig:tracker_model}
%\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The SVT is built in two separate halves that are mirror reflections of one another about the plane of 
the nominal electron beam.  Each half consists of five modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. 
The two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond 
the last layer that defines the nominal spacing between the upper and lower halves of the tracker.  A 
shaft attached to each support plate in front of layer 1 extends upstream and connects to a linear shift 
that transfers motion into the vacuum box through bellows to open and close the two halves around 
the dead zone. The C-support is mounted to an aluminum baseplate that defines the position of the 
SVT with respect to the vacuum chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both 
completed detector halves prior to final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
%\vspace*{-5mm}
\end{figure}
%=======================

\subsection{Components}
The sensors for the SVT are selected according to a number of requirements.  First, the sensors must be 
radiation tolerant to approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run.  This 
corresponds to about 4~MHz/mm$^2$, so the sensor and readout technology must be capable of handling 
very high local occupancies. Since sensitivity is limited by multiple scattering, a material budget of less 
than 1\% $X_0$/layer is imperative and far less is desirable. To achieve the required vertex resolution  
single-hit resolutions better than XXXX~$\mu$m are required. Finally, the sensor technology must 
be mature and readily available at low cost.  Silicon microstrips are the best match to these requirements, and 
a supply of appropriate microstrip sensors purchased from the Hamamatsu Photonics Corporation for the 
Run 2b upgrade of the D\O experiment~\cite{Denisov:2001aa} are readily available. 
These are $p+$-on-$n$, single sided, AC coupled, 
polysilicon-biased sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch 
over their $4\times10$~cm$^2$ surface. Although a maximum bias of 350~V is specified, the vast majority are 
operable to 1000~V and therefore remain fully depleted to a dose of approximately 
$1.5\times10^{14}$~\fluenceunit{}.

%\subsubsection{Front-end Electronics}
Because the regions of high occupancy are small spots in two dimensions, only a short length of any one 
strip see a significant occupancy, and the strips in that region act as long pixels. However, the rates are still 
very high and lowering the peak occupancy in the sensors to approximately 1\% for tracking requires a 
trigger window and tagging of hit times to roughly 8~ns.  The FADC 
readout for the ECal and muon system are capable of this (see Sec.~\ref{sec:fadc}), but achieving 
$2\sigma$ efficiency for 
silicon hits then requires 2~ns time resolution for the hits in the SVT. This performance can be achieved with 
the APV25 readout ASIC developed for the CMS experiment at CERN~\cite{French:2001xb}.  When 
operated in ``multi-peak mode", the APV25 captures successive samples of the output of the shaper in sets 
of three at a sampling rate of approximately 40~MHz.  
By fitting the known $CR$-$RC$ shaping curve to these samples, the initial time of the hit can be 
determined to a precision of 2~ns for S/N$>25$, an achievable figure with our sensors if read out 
individually~\cite{Friedl:2009zz}.  For the SVT, six-sample readout and the shortest possible shaping time 
(35~ns) will be used to best distinguish hits that overlap in time.
The APV25 ASICs are hosted on simple FR4 hybrids since these hybrids and their cooling system are 
outside the tracking volume.  Along with the sensors, these are assembled into half-modules, one for each 
tracking view, with a short cable pigtail to provide power and configuration to the modules and signal 
readout.

%\subsubsection{Support Structure and Cooling}

The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back around 
an aluminum cooling block at one end and a similar PEEK spacer block at the other. 
Figure~\ref{fig:tracker_module} shows a single module after assembly.
%=======================
\begin{figure}[htp]
	\begin{center}
   	 \includegraphics[width=7cm]{figures/IMG_5200}
	\caption{\small{A prototype module assembly (foreground) with the 50~mrad (left) and 100~mrad (right) module assembly fixtures in the background.  A pair of cooling blocks and a spacer block can be seen on the fixtures.} }
	\label{fig:tracker_module}
	\end{center}
\vspace*{-5mm}
\end{figure}
%=======================
The cooling block provides the primary mechanical support for the module as well as cooling via copper 
tubes pressed into grooves in the plates. The spacer block defines the spacing between the sensors at the 
far end of the module, stiffens the module structure, and improves the stability of the sensor alignments.

The total power consumption of the five APV25 chips mounted on 
the hybrid readout board is about 2~W. Since heating from the leakage current is only significant at a 
single small spot on the sensor, the 
dominant heat load on the sensor, even after irradiation, is radiant heat from the inside wall of the vacuum 
chamber, less than 0.5~W per sensor. The total power consumption budget of about 40~W is removed by a 
water/glycol mixture circulated through a flexible manifold attached to the cupper tubes in the cooling blocks. 
During the Test run the sensors where operated at around $23^{\circ}$C with a total mass flow of 
about XXXXg/s.

Each half module consists of a single sensor and a hybrid electronic readout board glued to a 
polyamide-laminated carbon fiber composite backing.  A window is machined in the carbon fiber leaving 
only a frame 
around the periphery of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to 
the surface of the carbon fiber with 1 mm overhang at all openings to ensure good isolation between the 
backside of the sensor, carrying high-voltage bias, and the carbon fiber which is held near ground.  The 
average support material in the tracking volume is approximately 0.06\% $X_{0}$ per double-sided module 
for a total material budget of 0.7\% per layer.

\subsection{Digitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT data acquisition (DAQ) based on the Reconfigurable Cluster Element (RCE) and Cluster 
Interconnect (CI) concept developed at SLAC as generic building blocks for DAQ systems in high energy 
physics. The RCE is a generic computational building block, housed on a separate daughter card called 
Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
(COB), see Fig.~\ref{fig:cob}.
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{Picture of the SVT DAQ COB board with four data processing daughter cards visible.}
	\label{fig:cob}
}
\end{center}
\end{figure}
The Gen-I RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the COB. 
A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to the sensitive 
range of a 14-bit ADC operating at the system clock of 41.667~MHz. 
The RTM is organized into four sections with each section supporting three SVT half-module hybrids (15 
APV25 channels). The RTM also includes a 4-channel Fiber Optic module and supporting logic which can be 
used to interface to the JLab trigger system supervisor.
Each section of the RTM, up to three hybrids, is input to a DPM which apply thresholds for data reduction and 
organizes the sample data into UDP datagrams. The DPM also hosts an I2C controller used to configure and 
monitor the APV25 chips on those three hybrids. A single ATCA crate with two COB cards was used, one 
supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as the trigger and data 
transmission module. The two COB cards and their DPMs are interconnected with a 10Gb/s switch 
card~\cite{Larsen:2011zb} which 
also hosts two 1Gb/s Ethernet interfaces to the external SVT DAQ PC.

The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low latency 
data reception card. The first Ethernet interface is used for slow control and monitoring of the 8 DPM modules. 
The second Ethernet interface serves as the interface to the JLAB data acquisition system. The third custom low 
latency network interface is used to receive data from the SVT ATCA crate and supports a low latency, reliable 
TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control and monitoring software 
as well as the JLab read out controller (ROC) application described in more detail in Sec.~\ref{sec:daq}.

This system is capable of operating up to 20~kHz and XXXX~MB/s which is well in line with the rates 
expected and observed during the HPS Test run.

@@

%Hybrid readout boards and half-modules were assembled at SLAC.  Mounting APV25 chips and all wirebonding and QA testing were performed at University of California, Santa Cruz.

Of the sensors tested during production, 90\% were capable of 1000~V bias voltage without breakdown. 
Hybrids underwent quick QA testing and each half-module was run at low temperature ($\approx5^{\circ}$ C) and 
fully characterized for pedestals, gains, noise and time response after assembly.  
%All 29 production modules were assembled between mid-February and the end of March, 2012.  Module yields were excellent for such a small production.  Of 165 APV chips acquired, 150 were used to assemble 30 production hybrids, of which 29 passed QA testing.  
Of 29 half-modules built, 28 passed 
QA testing, leaving 8 spare modules after completion of the SVT.  Full-module assembly and 
mechanical surveys were performed at SLAC
% in early April 2012 
before final assembly, testing and shipping of the SVT to JLab
% on April 11.  
A custom shipping container with nested crates and redundant isolation for shock and vibration 
%, based on experience from FNAL~\cite{shipping},
was built in order to safely send the partly assembled SVT to JLab. 
% The two fully assembled SVT halves were attached to a baseplate supported by four wire-rope isolators. This plate, covered by a lexan cover for cleanliness, was mounted inside an inner box surrounded by 4 inches of Polyurethane foam to complete the two-spring construction. 
At JLab, the entire SVT was integrated with the full DAQ and the power supplies 
%for the first time in the clean room, 
before moving the module-loaded support plates to Hall~B for final mechanical assembly and installation inside of the 
vacuum chamber.
% on April 19, 2012.

\subsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. The 
optical survey of individual modules with precision of a few $\mu$m are combined with a touch-probe survey 
of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the silicon sensor layers with 
respect to the support plates and the mechanical survey balls on the base plate.
After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate position 
inside the pair spectrometer vacuum chamber is used to determine the global position of the SVT with 
respect to CEBAF beam line. 
The resulting survey-based alignment has the position of the silicon sensors correct to within a few hundred 
microns. A more sophisticated global track-based alignment technique to reach the final alignment precision 
is being developed.

@@

The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the experiment: provides a trigger to DAQ system and 
is used in the analysis for electron identification. 
%The device is highly segmented. It is fast, able to readout at rates comparable to those in the tracker, and able to provide good spatial and energy information to the trigger electronics. Like the tracker, the electromagnetic calorimeter is split to avoid impinging on the “dead zone”. The beam and radiative secondaries pass between the two of the calorimeter in vacuum, to avoid generating unnecessary backgrounds.
%Step\subsection{Purpose and Design Requirements}
%StepThe electromagnetic calorimeter (ECal) provide the trigger for the data acquisition and will be used for electron identification during the data analysis. The ECal is positioned after the analyzing dipole magnet and cover the full acceptance region of the SVT. It consist of two halves, split in the horizontal beam plane. The gap between upper and lower parts, $XXXX$~mrad (15mrad for electron running),  as seen from the target location, is necessary to avoid the "dead zone" where occupancy and radiation prevents any instrumentation to be situated.  
The energy of electrons of interest in HPS experiment will be in the range 
$0.5-6.5$~GeV. The ECal modules must have sufficient radiation lengths to absorb the full energy of these 
scattered electrons, have fine enough granularity to handle a high rate of electromagnetic 
background and survive large doses of radiation, especially near the beam plane. In addition, it needs to 
have excellent hit time resolution, $<10$~ns, in order to beat down beam backgrounds.

@@

Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the “dead zone”. The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}. The beam and radiative secondaries pass between the two parts in vacuum, to avoid generating unnecessary backgrounds. The crystal modules in each part are arranged in rectangular formation, as shown in top panel of Fig.~\ref{fig:ecal}. There are 5 layers in each formation. Each layer has $46$ crystals except for the layers closest to the beam 
plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module assembly of each ECal part was enclosed inside a temperature controlled box.

>>>>

\subsection{Layout}
The layout of the SVT is summarized in Tab.~\ref{tab:trk} and rendered in Fig.~\ref{fig:tracker_model}. 
Each of the layers is comprised of a pair of closely-spaced silicon microstrip sensors mounted back-
to-back to form a module. A 100~mrad stereo angle is used in the first three layers to provide higher-
resolution 3D space points for vertexing.  Using 50~mrad in the last two layers breaks the tracking 
degeneracy of having five identical layers and minimizes fakes from ghost hits to improve pattern 
recognition. Altogether, the SVTcomprises 20 sensors for a total of 12780 readout channels. 
%=======================
\begin{center}
\begin{table}[ht]
{\footnotesize
\begin{tabular}{lccccc}   
\hline \hline 
    Layer & 1 & 2 & 3 & 4 & 5 \\      
\hline
    $z$ from target (cm)  & 10 & 20 & 30 & 50 & 70  \\ 
    Stereo angle (mrad)  & 100 & 100 & 100 & 50 & 50 \\ 
    Bend res. ($\mu$m)  & $\approx$60 & $\approx$60 & $\approx$60 & $\approx$120 & $\approx$120  \\ 
    Non-bend res. ($\mu$m)  & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6 & $\approx$6  \\ 
    \# of sensors  & 4 & 4 & 4 & 4 & 4  \\ 
    Dead zone (mm) & $\pm1.5$  & $\pm3.0$  & $\pm4.5$  & $\pm7.5$  & $\pm10.5$  \\ 
    Power cons. (W) & 6.9 & 6.9 & 6.9 & 6.9 & 6.9 \\
\hline \hline
\end{tabular}
\caption{\small Layout of the SVT.}
}
\label{tab:trk}
\vspace*{-15mm}
\end{table}
\end{center}
%=======================
\begin{center}
\begin{figure}[htp]
\includegraphics[width=7cm]{figures/HPS_nochamber}
\caption{\small A rendering of the SVT showing the modules on their support plates held by the 
hinged C-support on the left and the motion levers on the right. The sensors are shown in red and the 
hybrid readout boards in green. The beam enters from the right through a vacuum box with flanges 
for services. }
\label{fig:tracker_model}
%\vspace*{-5mm}
\end{figure}
\end{center}
%=======================
The SVT is built in two separate halves that are mirror reflections of one another about the plane of 
the nominal electron beam.  Each half consists of five modules mounted on a support plate that 
provides services to the modules and allows them to be moved as a group relative to the dead zone. 
The two halves of the tracker are connected to hinges mounted on a C-shaped support just beyond 
the last layer that defines the nominal spacing between the upper and lower halves of the tracker.  A 
shaft attached to each support plate in front of layer 1 extends upstream and connects to a linear shift 
that transfers motion into the vacuum box through bellows to open and close the two halves around 
the dead zone. The C-support is mounted to an aluminum baseplate that defines the position of the 
SVT with respect to the vacuum chamber. Figure~\ref{fig:tracker_halves} shows a photograph of both 
completed detector halves prior to final assembly. 
%=======================
\begin{figure}[htp]
\begin{center}
    \includegraphics[width=7cm]{figures/2012-101-PHOTON-DETECTOR-001}
\caption{\small{Both halves of the HPS Test SVT after final assembly at SLAC.  The cooling manifolds and 
integrated cable runs are clearly seen.} }
\label{fig:tracker_halves}
\end{center}
%\vspace*{-5mm}
\end{figure}
%=======================

\subsection{Components}
The sensors for the SVT are $p+$-on-$n$, single sided, AC coupled, polysilicon-biased microstrip 
sensors fabricated on $<100>$ silicon and have 30 (60) micron sense (readout) pitch over their 
$4\times10$~cm$^2$ surface. This sensor technology was selected to match the requirement of 
a $<1$\% $X_0$ per layer, single-hit resolution better than 50~$\mu$m and tolerant of a radiation 
dose of approximately $1.5\times10^{14}$~\fluenceunit{} for a six month run. The sensors 
were purchased from the Hamamatsu Photonics Corporation for the cancelled 
Run 2b upgrade of the D\O~experiment~\cite{Denisov:2001aa} which satisfied the requirement that 
the technology must be mature and available within the time and budget constraints.

%\subsubsection{Front-end Electronics}
Despite having only small spots with very high occupancy (up to 4~MHz/mm$^2$) closest to the primary 
beam, see Fig.~\ref{fig:radiation}, the rates are still high and lowering the peak occupancy to 
approximately 1\% for tracking requires a trigger window and hit time tagging of roughly 8~ns. The 
ECal readout and trigger described in Sec.~\ref{sec:fadc} can achieve such resolution. To reach this 
performance the sensors for the SVT are readout by the APV25 ASIC developed for the CMS 
experiment at CERN~\cite{French:2001xb}. The APV25 can capture two successive samples of three 
of the output of the shaper at a sampling rate of approximately 40~MHz.  By fitting the known 
$CR$-$RC$ shaping curve to these samples, the initial time of the hit can be determined to a precision 
of 2~ns for S/N$\approx25$~\cite{Friedl:2009zz}.  For electron beam running, six-sample readout and 
the shortest possible shaping time (35~ns) is used to best distinguish hits that overlap in time.
The APV25 ASICs are hosted on simple FR4 hybrid readout boards, outside the tracking volume, with a 
short twisted-pair pigtail cable to provide power and configuration and signal readout. Along with a 
single sensor, these are glued to a polyamide-laminated carbon fiber composite backing making 
up a half-module. A window is machined in the carbon fiber leaving only a frame around the periphery 
of the silicon to minimize material. A 50~$\mu$m sheet of polyamide is laminated to the surface of the 
carbon fiber with 1~mm overhang at all openings to ensure good isolation between the backside of the 
sensor, carrying high-voltage bias, and the carbon fiber which is held near ground.

The sensor modules for the SVT consist of a pair of identical half-modules, sandwiched back-to-back 
around an aluminum cooling block at one end and a similar PEEK spacer block at the other. 
Figure~\ref{fig:tracker_module} shows a single module after assembly.
%=======================
\begin{figure}[htp]
	\begin{center}
   	 \includegraphics[width=7cm]{figures/IMG_5200}
	\caption{\small{A prototype module assembly (foreground) with the 50~mrad (left) and 100~mrad (right) module assembly fixtures in the background.  A pair of cooling blocks and a spacer block can be seen on the fixtures.} }
	\label{fig:tracker_module}
	\end{center}
\vspace*{-5mm}
\end{figure}
%=======================
The cooling block provides the primary mechanical support for the module as well as cooling via copper 
tubes pressed into grooves in the plates. The spacer block defines the spacing between the sensors at 
the far end of the module, stiffens the module structure, and improves the stability of the sensor 
alignment.  The average support material in the tracking volume is approximately 0.06\% $X_{0}$ per 
double-sided module for a total material budget of 0.7\% per layer.

The total SVT power consumption budget of about 50~W is removed by a water/glycol mixture 
circulated through a flexible manifold attached to the copper tubes in the cooling blocks. During the Test 
run the sensors where operated at around $23^{\circ}$C. The power consumption is dominated by five 
APV25 ASICs on each hybrid board consuming approximately 2~W, radiant heat load is less than 
0.5~W per sensor and leakage current is only significant in a small spot after irradiation.

\subsection{Digitization, Event Building and Data Transmission}
\label{sec:svt_daq}
The SVT data acquisition (DAQ) is based on the Reconfigurable Cluster Element (RCE) and cluster 
interconnect concept developed at SLAC as generic building blocks for DAQ systems. 
The RCE is a generic computational building block, housed on a separate daughter card called 
Data Processing Module (DPM), that are realized on an ATCA front board called the Cluster On Board 
(COB), see Fig.~\ref{fig:cob}.
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{The SVT DAQ COB board with four data processing daughter cards visible on the left side.}
	\label{fig:cob}
}
\end{center}
\end{figure}
The first generation RCE used in the Test run consisted of a Virtex~5 FPGA with 1~GB of DDR3 RAM. 
A schematic overview of the system is shown in Fig.~\ref{fig:svtdaq}. 
 \begin{figure}[]
\begin{center}
{\small
	\includegraphics[width=6cm]{figures/svt_daq_module}
	\caption{Block diagram overview of the SVT DAQ.}
	\label{fig:svtdaq}
}
\end{center}
\end{figure}
The outputs of 12 SVT half-modules are digitized on the Rear-Transition-Module (RTM), a custom board 
on the back side of the ATCA crate, interfacing the HPS readout to the generic DAQ components on the 
COB. A pre-amplifier converts the APV25 differential current output to a different voltage output scaled to 
the sensitive range of a 14-bit ADC operating at the system clock of 41.667~MHz. The RTM is organized 
into four sections with each section supporting three SVT half-module hybrids (15 APV25 ASICs). The 
RTM also includes a 4-channel fiber optic module and supporting logic which is used to interface 
to the JLab trigger system supervisor. Each section of the RTM is input to a DPM which apply thresholds 
for data reduction and organizes the sample data into UDP datagrams. The DPM also hosts an I$^{2}$C 
controller used to configure and monitor the APV25 ASICs. A single ATCA crate with two COB cards 
was used, one supporting four DPMs and one supporting 3 DPMs and one DPM that is configured as 
the trigger and data transmission module. The two COB cards and their DPMs are interconnected with a 
10Gb/s switch card~\cite{Larsen:2011zb} which also hosts two 1Gb/s Ethernet interfaces to the external 
SVT DAQ PC.

The external PC supports three network interfaces; two standard 1Gb/s Ethernet and one custom low 
latency data reception card. The first is used for slow control and monitoring of the 8 
DPM modules and the second serves as the interface to the JLAB data acquisition system. The third 
custom low latency network interface is used to receive data from the ATCA crate and supports a low 
latency, reliable TTL trigger acknowledge interface to the trigger DPM. This PC hosts the SVT control 
and monitoring software as well as the JLab Read Out Controller (ROC) application described in more 
detail in Sec.~\ref{sec:daq}.

While trigger rates during the Test run was significantly lower this system was tested at trigger rates up 
to 20~kHz and 50~MB/s.

@@

%Of the sensors tested during production, 90\% were capable of 1000~V bias voltage without breakdown. 
Hybrids with APV25 ASICs underwent quick qualification testing and each half-module was run at low 
temperature ($\approx5^{\circ}$ C) and fully characterized for pedestals, gains, noise and time response 
after assembly.  Of 29 half-modules built, 28 passed qualification testing, leaving 8 spare modules after 
completion of the SVT, all capable of 1000~V bias voltage without breakdown.  Full-module assembly 
and mechanical surveys were performed at SLAC before final assembly, testing and shipping of the 
SVT to JLab. A custom shipping container with nested crates and redundant isolation for shock and 
vibration was built in order to safely send the partly assembled SVT to JLab. At JLab, the entire SVT was 
integrated with the full DAQ and the power supplies before moving the module-loaded support plates to 
Hall B for final mechanical assembly and installation inside of the vacuum chamber.

\subsection{Alignment}
The SVT was aligned using a combination of optical, laser and touch probe surveys at SLAC and JLab. 
The optical survey of individual modules with precision of a few $\mu$m are combined with a 
touch-probe survey of the overall SVT support structure, with 25-100~$\mu$m precision, to locate the 
silicon sensor layers with respect to the support plates and the mechanical survey balls on the base 
plate. After full assembly and installation of the SVT at JLab, a mechanical survey of the SVT base plate 
position inside the pair spectrometer vacuum chamber is used to determine the global position of the 
SVT with respect to CEBAF beam line. The resulting survey-based alignment has the position of the 
silicon sensors correct to within a few hundred microns measured from tracks in the Test run data. 
A more sophisticated global track-based alignment technique to reach final alignment precision 
well below 50~$\mu$m is being developed.

@@

The electromagnetic calorimeter, installed downstream of the tracker, performs two essential functions for the experiment: provides a trigger to DAQ system and 
is used in the analysis for electron identification. 
%The device is highly segmented. It is fast, able to readout at rates comparable to those in the tracker, and able to provide good spatial and energy information to the trigger electronics. Like the tracker, the electromagnetic calorimeter is split to avoid impinging on the Òdead zoneÓ. The beam and radiative secondaries pass between the two of the calorimeter in vacuum, to avoid generating unnecessary backgrounds.
%Step\subsection{Purpose and Design Requirements}
%StepThe electromagnetic calorimeter (ECal) provide the trigger for the data acquisition and will be used for electron identification during the data analysis. The ECal is positioned after the analyzing dipole magnet and cover the full acceptance region of the SVT. It consist of two halves, split in the horizontal beam plane. The gap between upper and lower parts, $XXXX$~mrad (15mrad for electron running),  as seen from the target location, is necessary to avoid the "dead zone" where occupancy and radiation prevents any instrumentation to be situated.  
The energy of electrons of interest in HPS experiment will be in the range 
$0.5-6.5$~GeV. The ECal modules must have sufficient radiation lengths to absorb the full energy of these 
scattered electrons, have fine enough granularity to handle a high rate of electromagnetic 
background and survive large doses of radiation, especially near the beam plane. In addition, it needs to 
have excellent hit time resolution, $<10$~ns, in order to beat down beam backgrounds.

@@

Like the tracker, the electromagnetic calorimeter is split into two parts, beam-up and beam-down, to avoid impinging on the Òdead zoneÓ. The two parts of the Ecal are separated by a vacuum chamber, see Fig.~\ref{fig:ecal}. The beam and radiative secondaries pass between the two parts in vacuum, to avoid generating unnecessary backgrounds. The crystal modules in each part are arranged in rectangular formation, as shown in top panel of Fig.~\ref{fig:ecal}. There are 5 layers in each formation. Each layer has $46$ crystals except for the layers closest to the beam 
plane where 9 modules were removed to allow a larger opening for the outgoing electron and photon beams. 
In order to have stable light yield from crystals, and stable operation of APDs and preamplifiers, the module assembly of each ECal part was enclosed inside a temperature controlled box.
